A sheaf--function dictionary for algebraic tori over local fields

### 2013-09-13 shanghai.tex
Small changes resulting from our conversation yesterday: Hmm removed; citation made more specific.

The category $\QC(G)$ of quasicharacter sheaves on $G$ is a rigid symmetric monoidal category
\cite{etingof:09a}*{\S~1.10} under the tensor product
$\qcs{L} \otimes \qcs{L'} \ceq (\gqcs{L}\otimes\gqcs{L'}, \mu\otimes\mu', \phi\otimes \phi')$,
with duals given by applying the sheaf hom functor 
$\sheafHom(\ - \ ,\EE)$.
The category of quasicharacter sheaves on $G$ is not abelian, so $\QC(G)$
is not a tensor category in the sense of \cite{deligne:02a}. \David{more specific citation}
This rigid monoidal category structure for $\QC(G)$ puts a group
structure on the set $\QCiso{G}$ of isomorphism classes in $\QC(G)$.
We now begin developing the tools to relate $\QCiso{G}$ to $\Hom(G(\Fq), \EEx)$.

@@

\Clifton{Now this section does mention quasicharacter sheaves.}
Although this section does not mention quasicharacter sheaves, 
we will need Proposition~\ref{prop:X} to prove our main result on quasicharacter sheaves, 
Theorem~\ref{thm:snake}.

@@

  The definition of $F_1$ depends 
  on the choice of a Néron model for every algebraic torus $T$.
  However, since Néron models are unique up to unique isomorphism,
  the isomorphism class of $\GN{T}_n$ is uniquely determined by $T$
  \Clifton{Hmmm}
  and the group of isomorphism classes of objects in $\QC(\GN{T}_n)$ 
  is uniquely determined by $T$. 
  To define $F_1$ on morphisms one uses the Néron mapping property.

@@

\begin{proof}
First, note that since $\Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})$ 
is a scheme over $\OK$, 
the Greenberg transform $\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)$ 
is obtained by base change along $\OK \to \OK/\pK^n$ 
followed by the Greenberg functor over the Artinian ring $\OK/\pK^n$. 
On the other hand, since $\underline{T'}$ is a scheme over $\mathcal{O}_{K'}$, 
the Greenberg transform $\Gr_{en}(\underline{T'})$ is defined by base change along 
$\mathcal{O}_{K'} \to \mathcal{O}_{K'}/\mathfrak{p}_{K'}^{en}$ 
followed by the Greenberg functor over the Artinian ring $\mathcal{O}_{K'}/\mathfrak{p}_{K'}^{en}$; 
see Definition~\ref{def:Grn}. 
Note also that 
\Clifton{I haven't checked this! Have you?}
\begin{equation}\label{nem}
\mathcal{O}_{K'} \otimes_{\OK} \OK/\pK^n \iso \mathcal{O}_{K'}/\mathfrak{p}_{K'}^{en}.
\end{equation}

>>>>

The category $\QC(G)$ of quasicharacter sheaves on $G$ is a rigid symmetric monoidal category
\cite{etingof:09a}*{\S~1.10} under the tensor product
$\qcs{L} \otimes \qcs{L'} \ceq (\gqcs{L}\otimes\gqcs{L'}, \mu\otimes\mu', \phi\otimes \phi')$,
with duals given by applying the sheaf hom functor 
$\sheafHom(\ - \ ,\EE)$.
The category of quasicharacter sheaves on $G$ is not abelian, so $\QC(G)$
is not a tensor category in the sense of \cite{deligne:02a}*{0.1}.
This rigid monoidal category structure for $\QC(G)$ puts a group
structure on the set $\QCiso{G}$ of isomorphism classes in $\QC(G)$.
We now begin developing the tools to relate $\QCiso{G}$ to $\Hom(G(\Fq), \EEx)$.

@@

Although the next proposition makes no mention quasicharacter sheaves, 
it has immediate application to the problem of finding all quasicharacter sheaves
on finitely generated etale group schemes, as we will see at the end of the section.

@@

  The definition of $F_1$ depends 
  on the choice of a Néron model for every algebraic torus $T$.
  However, since Néron models are unique up to unique isomorphism,
  the isomorphism class of $\GN{T}_n$ is uniquely determined by $T$
  and the group of isomorphism classes of objects in $\QC(\GN{T}_n)$ 
  is uniquely determined by $T$. 
  To define $F_1$ on morphisms one uses the Néron mapping property.

@@

\begin{proof}
First, note that since $\Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})$ 
is a scheme over $\OK$, 
the Greenberg transform $\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)$ 
is obtained by base change along $\OK \to \OK/\pK^n$ 
followed by the Greenberg functor over the Artinian ring $\OK/\pK^n$. 
On the other hand, since $\underline{T'}$ is a scheme over $\mathcal{O}_{K'}$, 
the Greenberg transform $\Gr_{en}(\underline{T'})$ is defined by base change along 
$\mathcal{O}_{K'} \to \mathcal{O}_{K'}/\mathfrak{p}_{K'}^{en}$ 
followed by the Greenberg functor over the Artinian ring $\mathcal{O}_{K'}/\mathfrak{p}_{K'}^{en}$; 
see Definition~\ref{def:Grn}. 
Note also that 
\begin{equation}\label{nem}
\mathcal{O}_{K'} \otimes_{\OK} \OK/\pK^n \iso \mathcal{O}_{K'}/\mathfrak{p}_{K'}^{en}.
\end{equation}
